Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-01 Paper/structure.tex
Delete thesis-related files that I don’t need for the paper
Supplement improvements
Use lualatex to dodge pdflatex memory issues with large pgf plots

\usepackage[hang, small, labelfont=bf, up, textfont=it]{caption} % Custom captions under/above tables and figures

@@

\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[utf8]{inputenc} % Required for inputting international characters

@@

\addbibresource{../Thesis.bib} % The filename of the bibliography
\renewcommand{\cite}[1]{\autocite{#1}}

>>>>

\usepackage[hang, small, labelfont=bf, up, textfont=it]{caption} % Custom captions under/above tables and figures
\usepackage{subcaption}

@@

\usepackage{fontspec} % Output font encoding for international characters
\usepackage{luatexbase} % Output font encoding for international characters

@@

\addbibresource{../RSVOptimization.bib} % The filename of the bibliography
\renewcommand{\cite}[1]{\autocite{#1}}
